---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Lindsey Wilson"
date: "4/20/23"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
library(robotstxt)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

### Exercise 10

Lets go ahead and wrangle our data to separate the `title` variable into `title` and `year`

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(" ) %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)
```
The reason we aren't concerned about the error messages here is that they all either indicate 1.) that there was extra information in the string we aren't concerned about capturing, or. 2.) that there were no parentheses at all in the string so there wasn't any date to capture. 


### Exercise 12

Let's skim our data:

```{r skim}
skim(uoe_art)
```

As we can see here, there are 115 pieces with artist info missing and 1431 pieces with year information missing.

### Exercise 13

```{r histogram}

ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 10)
```

Add exercise headings as needed.
