---
title: "Lab 08 - University of Edinburgh Art Collection"
author: "Lindsey Wilson"
date: "4/21/23"
output: github_document
---

### Load packages and data

```{r load-packages, message = FALSE}
library(tidyverse) 
library(skimr)
library(robotstxt)
```

```{r load-data, message = FALSE, eval = TRUE}
# Remove eval = FALSE or set it to TRUE once data is ready to be loaded
uoe_art <- read_csv("data/uoe-art.csv")
```

### Exercise 10

Lets go ahead and wrangle our data to separate the `title` variable into `title` and `year`

```{r separate-title-date, error = TRUE}
uoe_art <- uoe_art %>%
  separate(title, into = c("title", "date"), sep = "\\(" ) %>%
  mutate(year = str_remove(date, "\\)") %>% as.numeric()) %>%
  select(title, artist, year, link)
```
The reason we aren't concerned about the error messages here is that they all either indicate 1.) that there was extra information in the string we aren't concerned about capturing, or. 2.) that there were no parentheses at all in the string so there wasn't any date to capture. 


### Exercise 11

Let's skim our data:

```{r skim}
skim(uoe_art)
```

As we can see here, there are 115 pieces with artist info missing and 1431 pieces with year information missing.

### Exercise 12

```{r histogram}
ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 5)
```

It looks like we have one data point with a `year` value of 2, which causes the scaling issue on the x-axis. Filtering that piece out should fix the problem:

```{r histogram2}
uoe_art %>%
  filter(year > 5) %>%
  ggplot(aes(x = year)) +
  geom_histogram(binwidth = 5)
```

### Exercise 13

The title of the out of ordinary piece is "Death Mask (2) (1964)". Therefore, it looks like what happened is that our code split the title on the first opening parenthesis, and threw away the data after the first closing parenthesis. This captured the "2", but resulted in the "1964" being thrown away.

I've fixed the issue below.  If I did it right, the new histogram should look essentially just like the old one but without having to do any filtering first:

```{r corrected-visualization}
uoe_art <-  uoe_art %>%
  mutate(year = if_else(link == "https://collections.ed.ac.uk/art/record/21649?highlight=*:*",
                        1964,
                        uoe_art$year,
                        missing = NULL))

ggplot(uoe_art, aes(x = year)) +
  geom_histogram(binwidth = 5)
```

### Exercise 14

Next we want to know who the most commonly featured artist in the collection is. Generating a frequency table should let us answer that question:

```{r frequency, output.lines = 10}
freq <- table(uoe_art$artist) %>%
  sort(decreasing = TRUE) %>%
  data.frame()

head(freq)
```

It looks like (besides Unknown), Emma Gillies is the most commonly represented artist in the collection, with 177 pieces. This makes sense after some Googling: Gillies is from Edinburgh, and has had an exhibit of her work featured at the University of Edinburgh library.

### Exercise 15

Let's see how many exhibits contain the word "Child" in the title:

```{r child}
#create a vector containing whether or not each item has "child" in title
child <- uoe_art$title %>%
  str_detect("(?i)child") %>%
  as.vector()

# mutate uoe_art to add above vector as a column
uoe_art <- uoe_art %>%
  mutate(child_in_title = child)

#filter uoe_art and count the rows that make it through filter
uoe_art %>%
  filter(child_in_title == TRUE)
```

It looks like there are 11 items with "child" in the title!
